\documentclass[a4paper,10pt]{article}
%-----------------------------------------------------------
\usepackage[top=0.75in, bottom=0.75in, left=0.55in, right=0.85in]{geometry}
\usepackage{graphicx}
\usepackage{url}
\usepackage{palatino}
\usepackage{tabularx}
\fontfamily{SansSerif}
\selectfont

\usepackage[T1]{fontenc}
\usepackage
%[ansinew]
[utf8]
{inputenc}

\usepackage{color}
\definecolor{mygrey}{gray}{0.75}
\textheight=9.75in
\raggedbottom

\setlength{\tabcolsep}{0in}
\newcommand{\isep}{-2 pt}
\newcommand{\lsep}{-0.5cm}
\newcommand{\psep}{-0.6cm}
\renewcommand{\labelitemii}{$\circ$}

\pagestyle{empty}
%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\small \colorbox{mygrey}{\begin{minipage}{0.975\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[3]{
\begin{tabular*}{6.62in}{l @{\extracolsep{\fill}} r}
	\textsc{{\textbf{#1}}} & \textsc{\textit{[#2]}} \\
\end{tabular*}\vspace{-8pt}}
%-----------------------------------------------------------

\begin{document}
\hspace{0.5cm}\\[-0.2cm]

\textbf{Aditya Krishnakumar} \\
\indent 12/A Shivalik Bungalows, \\
\indent Nr. Anandnagar Cross Roads, Satellite,  \\
\indent Ahmedabad (GUJARAT, INDIA) - 380015\\
\indent Email-id : \textbf{me@beingadityak.com} \\
\indent Mobile No.: \textbf{+91 9825024057} \\

\resheading{\textbf{ACADEMIC DETAILS} }\\[\lsep]
\\ \\
%\begin{table}[ht!]
%\begin{center}
\indent \begin{tabular}{ l @{\hskip 0.15in} l @{\hskip 0.15in} l @{\hskip 0.15in} l @{\hskip 0.15in} l }
\hline
\textbf{Examination} & \textbf{University} & \textbf{Institute} & \textbf{Year} & \textbf{CPI/\%} \\
\hline
UnderGraduate Specialization: & \textit{Computer Engineering} \\
Graduation & DD University, Nadiad & DD University, Nadiad & 2018 & 7.9\\
\hline
\end{tabular}
%\end{center}
%\end{table}
\\ \\

\resheading{\textbf{FIELDS OF INTEREST} }\\[\lsep]
\begin{itemize}
\item \noindent Cloud Computing, DevOps Engineering, Software Engineering
\end{itemize}

\resheading{\textbf{TECHNICAL SKILLS} }\\[\lsep]
\begin{itemize}
\item \noindent \textbf{Languages} (Python, Bash),\textbf{Database} (PostgreSQL), \textbf{DevOps Tools} (Terraform, Ansible, Packer, Docker, Kubernetes), \textbf{Cloud Platforms} (Google Cloud, Amazon Web Services, Microsoft Azure).
\end{itemize}

\resheading{\textbf{MAJOR PROJECTS AND SEMINAR} }\\[\lsep]
\begin{itemize}
\item \textbf{Media Access Control Controling
} (Research Project) \\
 \emph{(Guide:Prof. Hubert F.
, May'13 - till date)} \\[-0.6cm]
	\begin{itemize}\itemsep \isep
	\item Objective :Performance analysis of HTTP web browsing traffic.
.
	\item Performance analysis will help in comparing different MAC protocols based on different network sce-
narios.

	\item Studied various papers related to different MAC protocols and now working on improving simulations.

	\end{itemize}

\item \textbf{Second Item.
} (M. Tech. Seminar) \\
 \emph{(Guide: Prof. John Doe
, Jan'14 - Aug'14)} \\[-0.6cm]
	\begin{itemize}\itemsep \isep
	\item First subitem.
	\item Second subitem.
	\end{itemize}
\end{itemize}

\resheading{\textbf{STRENGTHS} }\\[\lsep]
\begin{itemize}
\item \noindent Positive Attitude, Social Interaction, Hardworking.
\end{itemize}

\resheading{\textbf{INTEREST AND HOBBIES} }\\[\lsep]
\begin{itemize}
\item \noindent Solving Puzzles.
\item \noindent Playing Chess.

\end{itemize}

\end{document}
